\documentclass{letter}

\usepackage{geometry}
\geometry{margin=2cm} % adjust the margin size as needed

\usepackage[T1]{fontenc}
\usepackage{txfonts}


\address{\textbf{Arkadiy Klyukin}\\
San Francisco Bay Area, CA}

\signature{Your Name}

\begin{document}

\begin{letter}{\textbf{London Stock Exchange Group Talent Acquisition Team} \\
                % US Bank \\
                San Francisco, CA}


\opening{Dear LSEG Hiring Manager,}

I am writing to express my strong interest in the FX Sales Specialist position at London Stock Exchange Group, as advertised. With a solid background in quantitative finance, electronic trading, and software development, I am confident in my ability to drive sales and foster client relationships in the FX market.

In my previous role, I have extensive experience in providing liquidity to ECNs, cultivating relationships with key clients, and driving product adoption through electronic trading platforms. I have successfully developed and integrated electronic pricing engines, executed electronic client trades, and provided liquidity to corporate and retail customers through ECNs. My ability to identify and encourage new accounts and use prospecting tools has contributed to my consistent track record of providing a high level of customer service and achieving PnL goals.

I have been following the innovative work of London Stock Exchange Group in the FX market and am impressed by the company's commitment to driving adoption of new products and services. I am eager to contribute to the continued success of the company and am excited about the opportunity to leverage my skills and experience in this role.

Thank you for considering my application. I am looking forward to the possibility of contributing to the continued success of London Stock Exchange Group. I am available at your earliest convenience for an interview.

Sincerely,\\
Arkadiy Klyukin
\end{letter}

\end{document}