\documentclass{letter}

\usepackage{geometry}
\geometry{margin=2cm} % adjust the margin size as needed

\usepackage[T1]{fontenc}
\usepackage{txfonts}


\address{\textbf{Arkadiy Klyukin}\\
San Francisco Bay Area, CA}

\signature{Your Name}

\begin{document}

\begin{letter}{\textbf{Intel Talent Acquisition Team} \\
                % US Bank \\
                Santa Clara, CA}


\opening{Dear Intel Hiring Manager,}

I am writing to express my strong interest in the Treasury Manager, Hedging and Capital Markets role at Intel. With a proven track record in facilitating treasury transactions, and managing portfolios, I am confident in my ability to contribute effectively to the strategic goals of Intel's Treasury department.

In my previous role, worked in the Asset/Liability Management (ALM) department. One of my key achievements was improving allocations, hedging, and funding ratios through collaborative efforts with these teams. This involved identifying and interpreting statistical data to assess treasury books risks and developing and executing strategic and tactical allocation approaches that aligned with the long-term goals of the organization. Additionally, I played a pivotal role in technical and legal topics such as Libor Fallback protocol and SOFR transition. Worked closely with legal, and tax teams to ensure regulatory compliance and accurate financial reporting as well as navigating the legal and regulatory compliance framework, including ISDA and Dodd Frank requirements.

Additionally I successfully ran derivatives books, and developed advanced trading tools and infrastructure within the department. My experience in trading, risk management, and project leadership aligns closely with the responsibilities and qualifications outlined in the job description. I would like emphasize that I also played a key role in the development of IR Derivatives franchise; oversaw sales, trading and developers teams; worked extensively on front office processes development and particularly derivatives-management-part of it, including setting up from scratch and pricing models homologation and validation.

Furthermore, my certifications in quantitative finance, financial risk management, and securities essentials, combined with my skills in statistics, econometrics, and programming languages, position me as a strategic thinker with strong financial analysis and problem-solving skills, as required for the role at Intel.

I am particularly drawn to Intel's commitment to innovation and collaboration, and I am eager to contribute to the company's success by leveraging my expertise in electronic trading, risk management, and financial software.

I would welcome the opportunity to further discuss how my background, skills, and certifications can contribute to the Treasury team at Intel. Thank you for considering my application. I look forward to the possibility of contributing to Intel's continued success.

Sincerely,\\
Arkadiy Klyukin
\end{letter}

\end{document}