%-------------------------
% Resume in Latex
% Github : https://github.com/AA-Kl
%------------------------

\documentclass[letterpaper,hidelinks]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{etoolbox}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{kpfonts}
\usepackage{pifont}
\usepackage{ragged2e}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
%\fancyfoot{} %when no page numbering needed
%\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\renewcommand*\ttdefault{lmvtt}
\renewcommand*\familydefault{\ttdefault} %% Only if the base font of the document is to be typewriter style
\usepackage[T1]{fontenc}

% Adjust margins
\addtolength{\oddsidemargin}{-0.77in}
\addtolength{\evensidemargin}{-0.77in}
\addtolength{\textwidth}{1.55in}
\addtolength{\topmargin}{-0.8in}
\addtolength{\textheight}{1.5in}

\addtolength{\headwidth}{\marginparsep}
\addtolength{\headwidth}{35mm}
\fancyhead[R]{\small{Authorized to work\\ in the US, \\ Green Card}}
\fancyfoot[L]{\textit{\small{$\mathbb{}^\ast$ Successfully completed all three levels of the CFA program, currently in the process of obtaining membership}}}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{\vspace{-10pt}\bfseries\raggedright\Large\color{black}}{}{0em}{}[\color{black}\titlerule\vspace{-6pt}]

% Custom commands
\newcommand{\resumeItemRoutine}[1]{
  \item[\small\ding{223}]\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemProject}[1]{
  \item[\small\ding{51}]\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \text{\small#3} & \text{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%
%----------HEADING-----------------
\begin{center}
  \textbf{\Huge{Ark K, CFA$\mathbb{}^\ast$, CQF, FRM}\\} \\ \vspace{1pt}
  \small
  \faMobile* \hspace{.5pt} \href{tel:+16508888387}{650 888 8387}
  $|$
  \faAt \hspace{.5pt} \href{mailto:aa.auxiliarymail@gmail.com}{aa.auxiliarymail@gmail.com}
  $|$
  \faGlobeAmericas \hspace{.5pt} \href{https://aa-kl.github.io}{aa-kl.github.io}
  $|$
  \faGithub \hspace{.5pt} \href{https://github.com/aa-kl}{aa-kl}
  $|$
  \faLinkedinIn \hspace{.5pt} \href{https://www.linkedin.com/in/aa-kl}{aa-kl}
  $|$
  \faTelegramPlane \hspace{.5pt} \href{https://t.me/aa_tgm}{@aa\_tgm}
\end{center}
%-----------About-----------------	    
\vspace{-27pt}
\section{Summary}
{\hspace{0.1in}
\raggedright{\leftskip.11in
    % ========== Summary Text ==========
With a solid background in finance and trading, coupled with exceptional expertise in quantitative analysis, I bring a wealth of knowledge and skills that make me an ideal candidate for the AI Training for Finance role. My experience spans market-making, electronic client trades execution, liquidity provision, and risk management for various financial products including FX, IR, commodities, and derivatives. I have a proven track record in portfolio management, financial engineering, and developing innovative trading strategies and tools. I've also demonstrated effectiveness in translating complex financial data into actionable insights, providing strategic advisory services, and aligning cross-functional efforts towards achieving business objectives. As a tech-savvy professional, I'm adept at leveraging advanced technologies and analytical tools to drive efficiency and accuracy in trading operations. My professional achievements are underpinned by a solid educational background and certifications in quantitative finance and risk management
% ==================================    
    \\}
}
%-----------Experience-----------------
\vspace{-8pt}
\section{Experience}
\vspace{1pt}
\resumeSubHeadingListStart
\resumeSubheading
{\textbf{\large{GPB,}\small\normalfont{ one of the largest domestic banks with an extensive international market presence}}}{\textbf{Oct 2018 \textbf{--} Jan 2023}}
{\textbf{FX and IR Trader | Fixed Income, Currencies and Commodities desk, Capital Markets}}
{\textbf{Moscow, RF}}
\vspace{1pt}
\resumeItemListStart
    % ========== G_Bank Routine ==========
\resumeItemRoutine{Market-making and executing client transactions across multiple asset classes, including FX, IR, commodities, and derivatives.}
\resumeItemRoutine{Developing and optimizing in-house technology to improve trading efficiency and accuracy.}
\resumeItemRoutine{Conducting thorough market analysis to inform trading strategies and client advisories.}
\resumeItemRoutine{Collaborating with legal and tax teams to navigate complex topics such as Libor Fallback protocol and SOFR transition.}
\resumeItemRoutine{Managing and analyzing daily trading volumes and currency exposures to mitigate financial risk.}
\resumeItemRoutine{Providing expert advisory services on foreign exchange matters to influence strategic financial planning}
% ==================================
\vspace{2pt}\\
\hspace{-13pt}\textbf{Relevant Projects:}
\vspace{-3pt}
    % ========== G_Bank Projects ==========
\resumeItemProject{Led the implementation of Interest Rates Option pricing engine and new instruments pricing.}
\resumeItemProject{Developed IR pricing tools and launched providing liquidity in IR products.}
\resumeItemProject{Participated in the setup and integration of the front office system (Calypso) from scratch}
% ==================================
\resumeItemListEnd

\vspace{-6pt}
\hspace{0cm}
\vspace{-8pt}

\resumeSubheading
{\textbf{\large{PSB,}\small\normalfont{ one of the top privately held local banks, with cutting-edge technologies in trading}}}{\textbf{Nov 2012 \textbf{--} Sep 2018}}
{\textbf{e-FX Trader | electronic FX and Precious Metals trading desk}}
{\textbf{Moscow, RF}}
\vspace{1pt}
\resumeItemListStart
    % ========== P_Bank Routine ==========
\resumeItemRoutine{Electronic client trades execution and liquidity providing in G10, and CIS currencies (Short Term IR and FX Spot/FX Swaps).}
\resumeItemRoutine{Monitoring and managing risk in commodities transactions: energy, agricultural, metals flow trading.}
\resumeItemRoutine{Developing franchise relations with key clients and cultivating new relationships.}
\resumeItemRoutine{Managing and supervising the e-FX sales team and programmers, improving client outcomes}
% ==================================
\vspace{2pt}\\
\hspace{-13pt}\textbf{Relevant Projects:}
\vspace{-3pt}
    % ========== P_Bank Projects ==========
\resumeItemProject{Developed feeds collecting and smart order matching engine from scratch.}
\resumeItemProject{Established transition to UDP protocols and improved roundtrip dramatically.}
\resumeItemProject{Integrated statistical arbitrage algorithms into the order routing and matching circuit}
% ==================================
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-10pt}
\section{Education}
\vspace{1pt}
\resumeSubHeadingListStart
\resumeSubheading
{{CQF Institute, Fitch | Quantitative finance programm, Leading Professor: Dr. Paul Wilmott}}{London, UK\vspace{-2pt}}
{Quantitative Finance Charter}{Jan 2022 \textbf{--} Jul 2022\vspace{4pt}}
\resumeSubheading
{{New Economic School | Morgan Stanley programm, Rector: Dr. Sergey Guriev}}{Moscow, RF\vspace{-2pt}}
{Masters in Finance}{Sep 2013 \textbf{--} Jul 2015\vspace{4pt}}
\resumeSubheading
{{National Research Nuclear University "MEPHI" | Applied Maths in Economics programm}}{Moscow, RF\vspace{-2pt}}
{Economist Mathematician}{Sep 2007 \textbf{--} Jul 2012}
\resumeSubHeadingListEnd

%-----------CERTIFICATES-----------
\vspace{-4pt}
\section{Certificates}
\resumeSubHeadingListStart
\small{\item{
  \begin{tabularx}{0.96\textwidth} { 
     >{\centering\arraybackslash\hsize=.33\hsize}X 
    || >{\centering\arraybackslash\hsize=.26\hsize}X 
    || >{\centering\arraybackslash\hsize=.35\hsize}X  
    || >{\centering\arraybackslash\hsize=.23\hsize}X } 
    \textbf{CFA} Charter$\mathbb{}^\ast$, \textbf{CFA Institute} & 
    \textbf{FRM} Charter, \textbf{GARP} & 
    \textbf{CQF} Certificate, \textbf{CQF Institute} & 
    \textbf{SIE} Passed, \textbf{FINRA}
    % \textbf{SIE} Passed, \textbf{Series 7} Candidate, \textbf{FINRA}
  \end{tabularx}
% \begin{flushleft} SIE Passed, \textbf{FINRA} \end{flushleft}
% \begin{center} FRM Certified, \textbf{GARP} \end{center} 
% \begin{flushright} CFA Level III Candidate, \textbf{CFA Institute} \end{flushright}
% {SIE Passed, \textbf{FINRA}}  %\vspace{2pt}
% {FRM Certified, \textbf{GARP}}  %\vspace{2pt}
% {CFA Level III Candidate, \textbf{CFA Institute}} %$|$ \vspace{2pt}
}}
\resumeSubHeadingListEnd

%-----------Skills-----------------
\vspace{-11pt}
\section{Skills}
%\vspace{1pt}
\resumeSubHeadingListStart
\small{\item{
              % \textbf{{Soft:}}{ thorough attention to detail, team player, under pressure decisionmaking, multitasking, self-motivated to learn\\} %$|$ \vspace{2pt}
              \textbf{{Math:}}{ statistics, econometrics, quantitative finance, portfolio optimization, machine learning, reinforcement learning\\} %$|$ \vspace{2pt}
              \textbf{{Programming:}}{ C\#, Python, .NET, QuantLib, QuickFIX, sklearn, pyfolio, Git, WPF, sockets, multithreading, bash, SQL, VBA, \LaTeX\\} %$|$ %\vspace{2pt}
              \textbf{{Software:}}{ Numerix, Calypso, Murex, Misys Summit, Refinitiv, Bloomberg, Reuters Dealing, 360T, FXAll, FastMatch, Integral, MS Excel\\} %$|$ \vspace{2pt}
              \textbf{{Protocols:}}{ FIX, FAST, PLAZAII, Bloomberg API, numerous ECN APIs, Open AI API, SSH } %$|$ \vspace{2pt}
              \textbf{{Other Interests:}}{ PCB Design, 3D, Rowing} %$|$ %\vspace{2pt}
              %\textbf{Sports:}{ Rowing, Nordic Skiing} %$|$ %\vspace{2pt}
              %\textbf{Languages:}{ English (Professional), Russian (Native)}
        }}

\resumeSubHeadingListEnd
%-----------Awards-----------------
\vspace{-12pt}
\section{Awards}
\begin{description}%[font=$\bullet$]
  \item{Won trading competition "Algorithmus 2012", nomination "Stable Income" (highest sharpe ratio). \\Asset class: Equities. Strategy: fractal MA, B. Mandelbrot}  
\vspace{-3pt}
\end{description}

\end{document} 