\documentclass{letter}

\usepackage{geometry}
\geometry{margin=2cm} % adjust the margin size as needed

\usepackage[T1]{fontenc}
\usepackage{txfonts}


\address{\textbf{Arkadiy Klyukin}\\
936 Shoreline Dr\\
San Mateo, San Francisco Bay Area, CA}

\signature{Your Name}

\begin{document}

\begin{letter}{\textbf{US Bank Talent Acquisition Team} \\
                % US Bank \\
                San Francisco, CA}


\opening{Dear US Bank Hiring Manager,}

I am excited to apply for the FX and Derivatives Analyst position at US Bank. With six years of experience in market making, liquidity providing, and portfolio management in both Emerging and Developed markets currencies and IR derivatives, as well as extensive expertise in market infrastructure and coding, I am confident that I have the skills and experience necessary to excel in this role.

At previous companies, I was responsible for managing a portfolio of FX and IR derivatives and consistently exceeded PnL goals year over year. I also played a key role in the development of IR Derivatives products market section on the local exchange MOEX and served the ALM department to improve portfolios allocation and hedging.

In addition to my experience in market making and portfolio management, I have extensive experience in programming and have used VBA to develop pricing tools and improve trading tools and desk infrastructure. For example, I developed a VBA-based pricing tool for FX options that allowed for quick and accurate pricing of complex option structures. I also used VBA to automate various trading tasks, such as order entry and risk management.

I am confident that my experience and skills make me an excellent candidate for the FX and Derivatives Analyst position at US Bank. Thank you for considering my application, I look forward to the opportunity to discuss my qualifications further.

I hold a valid work visa L2S and am authorized to work for any employer in the US.

Sincerely,\\
Arkadiy Klyukin
\end{letter}

\end{document}