%-------------------------
% Resume in Latex
% Author : Arkadiy Klyukin
% Github : https://github.com/AA-Kl
%------------------------

\documentclass[letterpaper,hidelinks]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{etoolbox}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{kpfonts}
\usepackage{pifont}
\usepackage{ragged2e}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
%\fancyfoot{} %when no page numbering needed
%\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\renewcommand*\ttdefault{lmvtt}
\renewcommand*\familydefault{\ttdefault} %% Only if the base font of the document is to be typewriter style
\usepackage[T1]{fontenc}

% Adjust margins
\addtolength{\oddsidemargin}{-0.77in}
\addtolength{\evensidemargin}{-0.77in}
\addtolength{\textwidth}{1.55in}
\addtolength{\topmargin}{-0.8in}
\addtolength{\textheight}{1.5in}

\addtolength{\headwidth}{\marginparsep}
\addtolength{\headwidth}{35mm}
\fancyhead[R]{\small{Authorized to work\\ in the US, \\ Green Card}}
\fancyhead[L]{\small{\underline{Talent Acquisition}\\ \underline{Manager Version}\\}}
\fancyfoot[L]{\textit{\small{$\mathbb{}^\ast$ Successfully completed all three levels of the CFA program, currently in the process of obtaining membership}}}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{\vspace{-10pt}\bfseries\raggedright\Large\color{black}}{}{0em}{}[\color{black}\titlerule\vspace{-6pt}]

% Custom commands
\newcommand{\resumeItemRoutine}[1]{
  \item[\small\ding{223}]\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemProject}[1]{
  \item[\small\ding{51}]\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \text{\small#3} & \text{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%
%----------HEADING-----------------

\begin{center}
  \textbf{\Huge{Arkadiy Klyukin, CFA$\mathbb{}^\ast$, CQF, FRM}\\} \\ \vspace{1pt}
  \small
  \faMobile* \hspace{.5pt} \href{tel:+16508888387}{650 888 8387}
  $|$
  \faAt \hspace{.5pt} \href{mailto:arkadiy.klyukin@gmail.com}{arkadiy.klyukin@gmail.com}
  $|$
  \faGlobeAmericas \hspace{.5pt} \href{https://aa-kl.github.io}{aa-kl.github.io}
  $|$
  \faGithub \hspace{.5pt} \href{https://github.com/aa-kl}{aa-kl}
  $|$
  \faLinkedinIn \hspace{.5pt} \href{https://www.linkedin.com/in/aa-kl}{aa-kl}
  $|$
  \faTelegramPlane \hspace{.5pt} \href{https://t.me/aa_tgm}{@aa\_tgm}
\end{center}
%-----------About-----------------	  
\vspace{-27pt}
\section{Summary}
{\hspace{0.1in}
\raggedright{\leftskip.11in
    % ========== Summary Text ==========
Bringing forth a strong background in quantitative finance and derivatives trading, I specialize in managing portfolios, executing client transactions, and providing liquidity in various asset classes. Leveraging my skills in data interpretation, risk assessment, and trade strategy development, I have consistently optimized profitability and reduced financial risk. I have an extensive track record of meeting performance indicators, fostering growth, and maintaining market dominance. Skilled in enhancing trading tools and infrastructure, I have improved efficiency and trade accuracy. My expertise extends to negotiating derivative trading legal frameworks and collaborating with cross-functional teams to ensure process alignment and regulatory compliance. I possess a deep understanding of asset and derivative pricing, coupled with a strong ability to operate well in a team environment, manage concurrent projects, and adapt quickly to new methods
% ==================================    
    \\}
}
%-----------Experience-----------------
\vspace{-8pt}
\section{Experience}
\vspace{1pt}
\resumeSubHeadingListStart
\resumeSubheading
{\textbf{\large{Gazprombank,}\small\normalfont{ one of the largest domestic banks with an extensive international market presence}}}{\textbf{Oct 2018 \textbf{--} Jan 2023}}
{\textbf{Derivatives Trader | Fixed Income, Currencies and Commodities desk, Capital Markets}}
{\textbf{Moscow, RF}}
\vspace{1pt}
\resumeItemListStart
    % ========== G_Bank Routine ==========
\resumeItemRoutine{Market making and executing client transactions in various currencies for FX spot, FX Derivatives (Options and Forwards), STIR, and xCCY transactions.}
\resumeItemRoutine{Providing liquidity in precious metals and commodities for forwards, futures, and options transactions.}
\resumeItemRoutine{Conducting thorough market analysis and presenting findings to management, sales teams, and clients.}
\resumeItemRoutine{Interpreting statistical data to assess trade risk and generating trade ideas.}
\resumeItemRoutine{Improving trading tools and desk infrastructure by developing and optimizing in-house technology.}
\resumeItemRoutine{Working with legal and tax teams on technical topics such as Libor Fallback protocol and SOFR transition, ISDA, Dodd Frank legal/regulatory compliance framework}
% ==================================
\vspace{2pt}\\
\hspace{-13pt}\textbf{Relevant Projects:}
\vspace{-3pt}
    % ========== G_Bank Projects ==========
\resumeItemProject{Implemented a new Interest Rates Option pricing engine.}
\resumeItemProject{Launched new instruments pricing and liquidity providing, adhering to ISDA regulations.}
\resumeItemProject{Developed and integrated electronic pricing engine, achieving PnL goals, and top market share}
% ==================================
\resumeItemListEnd

\vspace{-6pt}
\hspace{0cm}
\vspace{-8pt}

\resumeSubheading
{\textbf{\large{Promsvyazbank,}\small\normalfont{ one of the top privately held local banks, with cutting-edge technologies in trading}}}{\textbf{Nov 2012 \textbf{--} Sep 2018}}
{\textbf{e-FX Trader | electronic FX and Precious Metals trading desk}}
{\textbf{Moscow, RF}}
\vspace{1pt}
\resumeItemListStart
    % ========== P_Bank Routine ==========
\resumeItemRoutine{Executed electronic client trades and provided liquidity in G10 and CIS currencies.}
\resumeItemRoutine{Monitored and managed risks in commodities transactions: energy, agricultural, metals flow trading.}
\resumeItemRoutine{Developed franchise relationships with key clients, ensuring the best client experience}
% ==================================
\vspace{2pt}\\
\hspace{-13pt}\textbf{Relevant Projects:}
\vspace{-3pt}
    % ========== P_Bank Projects ==========
\resumeItemProject{Developed a feeds collecting and smart order matching engine from scratch.}
\resumeItemProject{Added short term IR liquidity providing/absorbing to/from WL single-bank platform.}
\resumeItemProject{Developed a proprietary client-server trading application for FX basket trading}
% ==================================
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-10pt}
\section{Education}
\vspace{1pt}
\resumeSubHeadingListStart
\resumeSubheading
{{CQF Institute, Fitch | Quantitative finance programm, Leading Professor: Dr. Paul Wilmott}}{London, UK\vspace{-2pt}}
{Quantitative Finance Charter}{Jan 2022 \textbf{--} Jul 2022\vspace{4pt}}
\resumeSubheading
{{New Economic School | Morgan Stanley programm, Rector: Dr. Sergey Guriev}}{Moscow, RF\vspace{-2pt}}
{Masters in Finance}{Sep 2013 \textbf{--} Jul 2015\vspace{4pt}}
\resumeSubheading
{{National Research Nuclear University "MEPHI" | Applied Maths in Economics programm}}{Moscow, RF\vspace{-2pt}}
{Economist Mathematician}{Sep 2007 \textbf{--} Jul 2012}
\resumeSubHeadingListEnd

%-----------CERTIFICATES-----------
\vspace{-4pt}
\section{Certificates}
\resumeSubHeadingListStart
\small{\item{
  \begin{tabularx}{0.96\textwidth} { 
     >{\centering\arraybackslash\hsize=.33\hsize}X 
    || >{\centering\arraybackslash\hsize=.26\hsize}X 
    || >{\centering\arraybackslash\hsize=.35\hsize}X  
    || >{\centering\arraybackslash\hsize=.23\hsize}X } 
    \textbf{CFA} Charter$\mathbb{}^\ast$, \textbf{CFA Institute} & 
    \textbf{FRM} Charter, \textbf{GARP} & 
    \textbf{CQF} Certificate, \textbf{CQF Institute} & 
    \textbf{SIE} Passed, \textbf{FINRA}
    % \textbf{SIE} Passed, \textbf{Series 7} Candidate, \textbf{FINRA}
  \end{tabularx}
% \begin{flushleft} SIE Passed, \textbf{FINRA} \end{flushleft}
% \begin{center} FRM Certified, \textbf{GARP} \end{center} 
% \begin{flushright} CFA Level III Candidate, \textbf{CFA Institute} \end{flushright}
% {SIE Passed, \textbf{FINRA}}  %\vspace{2pt}
% {FRM Certified, \textbf{GARP}}  %\vspace{2pt}
% {CFA Level III Candidate, \textbf{CFA Institute}} %$|$ \vspace{2pt}
}}
\resumeSubHeadingListEnd

%-----------Skills-----------------
\vspace{-11pt}
\section{Skills}
%\vspace{1pt}
\resumeSubHeadingListStart
\small{\item{
              % \textbf{{Soft:}}{ thorough attention to detail, team player, under pressure decisionmaking, multitasking, self-motivated to learn\\} %$|$ \vspace{2pt}
              \textbf{{Math:}}{ statistics, econometrics, quantitative finance, portfolio optimization, machine learning, reinforcement learning\\} %$|$ \vspace{2pt}
              \textbf{{Programming:}}{ C\#, Python, .NET, QuantLib, QuickFIX, sklearn, pyfolio, Git, WPF, sockets, multithreading, bash, SQL, VBA, \LaTeX\\} %$|$ %\vspace{2pt}
              \textbf{{Software:}}{ Numerix, Calypso, Murex, Misys Summit, Refinitiv, Bloomberg, Reuters Dealing, 360T, FXAll, FastMatch, Integral, MS Excel\\} %$|$ \vspace{2pt}
              \textbf{{Protocols:}}{ FIX, FAST, PLAZAII, Bloomberg API, numerous ECN APIs, Open AI API, SSH } %$|$ \vspace{2pt}
              \textbf{{Other Interests:}}{ PCB Design, 3D, Rowing} %$|$ %\vspace{2pt}
              %\textbf{Sports:}{ Rowing, Nordic Skiing} %$|$ %\vspace{2pt}
              %\textbf{Languages:}{ English (Professional), Russian (Native)}
        }}

\resumeSubHeadingListEnd
%-----------Awards-----------------
\vspace{-12pt}
\section{Awards}
\begin{description}%[font=$\bullet$]
  \item{Won trading competition "Algorithmus 2012", nomination "Stable Income" (highest sharpe ratio). \\Asset class: Equities. Strategy: fractal MA, B. Mandelbrot}  
\vspace{-3pt}
\end{description}

\end{document} 