%-------------------------
% Resume in Latex
% Author : Arkadiy Klyukin
% Github : https://github.com/AA-Kl
%------------------------

\documentclass[letterpaper,hidelinks]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{etoolbox}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{kpfonts}
\usepackage{pifont}
\usepackage{ragged2e}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
%\fancyfoot{} %when no page numbering needed
%\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\renewcommand*\ttdefault{lmvtt}
\renewcommand*\familydefault{\ttdefault} %% Only if the base font of the document is to be typewriter style
\usepackage[T1]{fontenc}

% Adjust margins
\addtolength{\oddsidemargin}{-0.77in}
\addtolength{\evensidemargin}{-0.77in}
\addtolength{\textwidth}{1.55in}
\addtolength{\topmargin}{-0.8in}
\addtolength{\textheight}{1.5in}

\addtolength{\headwidth}{\marginparsep}
\addtolength{\headwidth}{35mm}
\fancyhead[R]{\small{Authorized to work\\ in the US, \\ Green Card}}
\fancyfoot[L]{\textit{\small{$\mathbb{}^\ast$ Successfully completed all three levels of the CFA program, currently in the process of obtaining membership}}}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{\vspace{-10pt}\bfseries\raggedright\Large\color{black}}{}{0em}{}[\color{black}\titlerule\vspace{-6pt}]

% Custom commands
\newcommand{\resumeItemRoutine}[1]{
  \item[\small\ding{223}]\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemProject}[1]{
  \item[\small\ding{51}]\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \text{\small#3} & \text{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%
%----------HEADING-----------------
\begin{center}
  \textbf{\Huge{Arkadiy Klyukin, CFA$\mathbb{}^\ast$, CQF, FRM}\\} \\ \vspace{1pt}
  \small
  \faMobile* \hspace{.5pt} \href{tel:+16508888387}{650 888 8387}
  $|$
  \faAt \hspace{.5pt} \href{mailto:arkadiy.klyukin@gmail.com}{arkadiy.klyukin@gmail.com}
  $|$
  \faGlobeAmericas \hspace{.5pt} \href{https://aa-kl.github.io}{aa-kl.github.io}
  $|$
  \faGithub \hspace{.5pt} \href{https://github.com/aa-kl}{aa-kl}
  $|$
  \faLinkedinIn \hspace{.5pt} \href{https://www.linkedin.com/in/aa-kl}{aa-kl}
  $|$
  \faTelegramPlane \hspace{.5pt} \href{https://t.me/aa_tgm}{@aa\_tgm}
\end{center}
%-----------About-----------------	    
\vspace{-27pt}
\section{Summary}
{\hspace{0.1in}
\raggedright{\leftskip.11in
    % ========== Summary Text ==========
A dynamic, results-driven, and highly experienced trading, risk management, and financial engineering professional, leveraging comprehensive expertise in the development and execution of strategic trading and risk management frameworks. Exhibiting a strong track record of success in managing complex portfolios, delivering innovative trading solutions, and achieving superior financial outcomes. Demonstrated proficiency in quantitative finance, econometrics, and machine learning, coupled with exceptional command over various programming languages, trading platforms, and financial tools. Armed with CQF, FRM, SIE, and CFA certifications, reflecting advanced industry knowledge and technical prowess. Seeking a challenging role as a Capital Markets Lead to apply unparalleled skills in structuring and executing deals, driving business growth, and building strategic relationships
% ==================================    
    \\}
}
%-----------Experience-----------------
\vspace{-8pt}
\section{Experience}
\vspace{1pt}
\resumeSubHeadingListStart
\resumeSubheading
{\textbf{\large{Gazprombank,}\small\normalfont{ one of the largest domestic banks with an extensive international market presence}}}{\textbf{Oct 2018 \textbf{--} Jan 2023}}
{\textbf{Interest Rates Trader | Fixed Income, Currencies and Commodities desk, Capital Markets}}
{\textbf{Moscow, RF}}
\vspace{1pt}
\resumeItemListStart
    % ========== G_Bank Routine ==========
\resumeItemRoutine{Managed market-making operations, executing client transactions and providing liquidity in G10, EMEA, and CIS currencies for FX spot, FX Derivatives (Options and Forwards), STIR, and xCCY transactions, IR Options (Caps/Floors), and Forward Rate Agreements.}
\resumeItemRoutine{Conducted market analysis, interpreting statistical data to assess trade risk, and generating and executing innovative trade ideas.}
\resumeItemRoutine{Persistently surpassed PnL and market share KPIs, contributing substantially to growth and market positioning.}
\resumeItemRoutine{Utilized advanced statistical analysis techniques to evaluate trade risk, leading to the development and execution of trades that outperformed market benchmarks.}
\resumeItemRoutine{Led the enhancement of trading tools, utilizing Python, C#, Bloomberg API, ECN APIs, and SQL to significantly improve trade accuracy and reduce latency}
% ==================================
\vspace{2pt}\\
\hspace{-13pt}\textbf{Relevant Projects:}
\vspace{-3pt}
    % ========== G_Bank Projects ==========
\resumeItemProject{Implemented Interest Rates Option pricing engine with volatility surface calibration.}
\resumeItemProject{Launched new instruments pricing and liquidity providing, navigating ISDA regulations.}
\resumeItemProject{Developed IR pricing tools, launched providing liquidity in IR products to Bloomberg screen and bbti (C#, VBA, Bbg API).}
\resumeItemProject{Participated in the setup and integration of front office system (Calypso) from scratch}
% ==================================
\resumeItemListEnd

\vspace{-6pt}
\hspace{0cm}
\vspace{-8pt}

\resumeSubheading
{\textbf{\large{Promsvyazbank,}\small\normalfont{ one of the top privately held local banks, with cutting-edge technologies in trading}}}{\textbf{Nov 2012 \textbf{--} Sep 2018}}
{\textbf{e-FX Trader | electronic FX and Precious Metals trading desk}}
{\textbf{Moscow, RF}}
\vspace{1pt}
\resumeItemListStart
    % ========== P_Bank Routine ==========
\resumeItemRoutine{Led electronic client trades execution and liquidity providing in G10 and CIS currencies, managing risk in commodities transactions.}
\resumeItemRoutine{Achieved PnL goals, developed and integrated an electronic pricing engine which led to commanding market share.}
\resumeItemRoutine{Managed and supervised a team, improving client outcomes and business aspects of electronic trading}
% ==================================
\vspace{2pt}\\
\hspace{-13pt}\textbf{Relevant Projects:}
\vspace{-3pt}
    % ========== P_Bank Projects ==========
\resumeItemProject{Developed feeds collecting and smart order matching engine from scratch (C#, FIX, SQL).}
\resumeItemProject{Integrated statistical arbitrage algorithms into the order routing and matching circuit.}
\resumeItemProject{Developed proprietary client-server trading application for FX basket trading (FIX, Sockets, WPF)}
% ==================================
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-10pt}
\section{Education}
\vspace{1pt}
\resumeSubHeadingListStart
\resumeSubheading
{{CQF Institute, Fitch | Quantitative finance programm, Leading Professor: Dr. Paul Wilmott}}{London, UK\vspace{-2pt}}
{Quantitative Finance Charter}{Jan 2022 \textbf{--} Jul 2022\vspace{4pt}}
\resumeSubheading
{{New Economic School | Morgan Stanley programm, Rector: Dr. Sergey Guriev}}{Moscow, RF\vspace{-2pt}}
{Masters in Finance}{Sep 2013 \textbf{--} Jul 2015\vspace{4pt}}
\resumeSubheading
{{National Research Nuclear University "MEPHI" | Applied Maths in Economics programm}}{Moscow, RF\vspace{-2pt}}
{Economist Mathematician}{Sep 2007 \textbf{--} Jul 2012}
\resumeSubHeadingListEnd

%-----------CERTIFICATES-----------
\vspace{-4pt}
\section{Certificates}
\resumeSubHeadingListStart
\small{\item{
  \begin{tabularx}{0.96\textwidth} { 
     >{\centering\arraybackslash\hsize=.33\hsize}X 
    || >{\centering\arraybackslash\hsize=.26\hsize}X 
    || >{\centering\arraybackslash\hsize=.35\hsize}X  
    || >{\centering\arraybackslash\hsize=.23\hsize}X } 
    \textbf{CFA} Charter$\mathbb{}^\ast$, \textbf{CFA Institute} & 
    \textbf{FRM} Charter, \textbf{GARP} & 
    \textbf{CQF} Certificate, \textbf{CQF Institute} & 
    \textbf{SIE} Passed, \textbf{FINRA}
    % \textbf{SIE} Passed, \textbf{Series 7} Candidate, \textbf{FINRA}
  \end{tabularx}
% \begin{flushleft} SIE Passed, \textbf{FINRA} \end{flushleft}
% \begin{center} FRM Certified, \textbf{GARP} \end{center} 
% \begin{flushright} CFA Level III Candidate, \textbf{CFA Institute} \end{flushright}
% {SIE Passed, \textbf{FINRA}}  %\vspace{2pt}
% {FRM Certified, \textbf{GARP}}  %\vspace{2pt}
% {CFA Level III Candidate, \textbf{CFA Institute}} %$|$ \vspace{2pt}
}}
\resumeSubHeadingListEnd

%-----------Skills-----------------
\vspace{-11pt}
\section{Skills}
%\vspace{1pt}
\resumeSubHeadingListStart
\small{\item{
              % \textbf{{Soft:}}{ thorough attention to detail, team player, under pressure decisionmaking, multitasking, self-motivated to learn\\} %$|$ \vspace{2pt}
              \textbf{{Math:}}{ statistics, econometrics, quantitative finance, portfolio optimization, machine learning, reinforcement learning\\} %$|$ \vspace{2pt}
              \textbf{{Programming:}}{ C\#, Python, .NET, QuantLib, QuickFIX, sklearn, pyfolio, Git, WPF, sockets, multithreading, bash, SQL, VBA, \LaTeX\\} %$|$ %\vspace{2pt}
              \textbf{{Software:}}{ Numerix, Calypso, Murex, Misys Summit, Refinitiv, Bloomberg, Reuters Dealing, 360T, FXAll, FastMatch, Integral, MS Excel\\} %$|$ \vspace{2pt}
              \textbf{{Protocols:}}{ FIX, FAST, PLAZAII, Bloomberg API, numerous ECN APIs, Open AI API, SSH } %$|$ \vspace{2pt}
              \textbf{{Other Interests:}}{ PCB Design, 3D, Rowing} %$|$ %\vspace{2pt}
              %\textbf{Sports:}{ Rowing, Nordic Skiing} %$|$ %\vspace{2pt}
              %\textbf{Languages:}{ English (Professional), Russian (Native)}
        }}

\resumeSubHeadingListEnd
%-----------Awards-----------------
\vspace{-12pt}
\section{Awards}
\begin{description}%[font=$\bullet$]
  \item{Won trading competition "Algorithmus 2012", nomination "Stable Income" (highest sharpe ratio). \\Asset class: Equities. Strategy: fractal MA, B. Mandelbrot}  
\vspace{-3pt}
\end{description}

\end{document} 