\documentclass{letter}

\usepackage{geometry}
\geometry{margin=2cm} % adjust the margin size as needed

\usepackage[T1]{fontenc}
\usepackage{txfonts}


\address{\textbf{Arkadiy Klyukin}\\
San Francisco Bay Area, CA}

\signature{Your Name}

\begin{document}

\begin{letter}{\textbf{Wells Fargo Talent Acquisition Team} \\
                % Nomura \\
                Charlotte, NC}


\opening{Dear Wells Fargo Hiring Manager,}

I am writing to express my strong interest in the Interest Rate Derivatives Middle Office position at Wells Fargo, as advertised. With a solid background in Capital Markets industry experience and a proven track record of exceeding performance metrics, I am confident in my ability to contribute effectively to your team and support the growth of your business.

In my previous roles, I successfully facilitated client transactions, managed portfolios, and developed advanced trading tools and infrastructure. My experience in market making, risk management, and project leadership aligns closely with the responsibilities and qualifications outlined in the job description. I would like emphasize that I worked extensively with Calypso front office system and particularly derivatives-management-part of it, including setting up from scratch and pricing models homologation and validation. Additionally, my certifications in quantitative finance, financial risk management, and securities essentials, along with my proficiency in programming languages and financial software, further validate my qualifications for this role.

I am particularly drawn to the opportunity to collaborate with various business partners and contribute to the development of processes and procedures to support a growing business, as mentioned in the job description. I am confident that my skills in statistics, econometrics, and quantitative finance, combined with my ability to lead projects and mentor less experienced analysts, make me a strong fit for this position.

I am eager to bring my expertise and passion for the Capital Markets industry to Wells Fargo and contribute to its continued success. I am looking forward to the opportunity to discuss how my background, skills, and certifications align with the needs of your team in more detail.

Thank you for considering my application. I am excited about the possibility of joining your team and contributing to the continued success of Wells Fargo.

Sincerely,\\
Arkadiy Klyukin
\end{letter}

\end{document}