\documentclass{letter}

\usepackage{geometry}
\geometry{margin=2cm} % adjust the margin size as needed

\usepackage[T1]{fontenc}
\usepackage{txfonts}


\address{\textbf{Arkadiy Klyukin}\\
San Francisco Bay Area, CA}

\signature{Your Name}

\begin{document}

\begin{letter}{\textbf{New York Life Investments Talent Acquisition Team} \\
                % Nomura \\
                New York, NY}


\opening{Dear New York Life Investments Hiring Manager,}

I am writing to express my strong interest in the Derivatives Senior Associate position at New York Life Investments, as advertised. With a Bachelor's degree in Financial Engineering and over 5 years of experience in interest rate, equity, and currency derivatives, I am confident in my ability to contribute effectively to your team.

In my previous role, I facilitated derivative transactions by providing liquidity in multiple currencies and managed portfolios while consistently exceeding PnL and market share KPIs. Additionally, I have extensive experience in electronic trading, risk management, and the development of trading tools and infrastructure.

I am particularly proud of my involvement in projects such as the implementation of Interest Rates Option pricing engine and the launch of new instruments pricing and liquidity providing. These experiences have honed my skills in quantitative finance, programming, and innovation in the electronic trading space.

I hold certifications in quantitative finance, financial risk management, and I am a CFA Level 3 candidate, demonstrating my commitment to professional development and expertise in the financial domain.

I am excited about the opportunity to bring my unique blend of skills and experiences to New York Life Investments and contribute to the success of your team. I am confident that my background aligns well with the responsibilities and qualifications outlined in the job description.

Thank you for considering my application. I am looking forward to the possibility of contributing to your team and would welcome the opportunity to further discuss how my background, skills, and certifications can benefit New York Life Investments.

Sincerely,\\
Arkadiy Klyukin
\end{letter}

\end{document}
