\documentclass{letter}

\usepackage{geometry}
\geometry{margin=2cm} % adjust the margin size as needed

\usepackage[T1]{fontenc}
\usepackage{txfonts}


\address{\textbf{Arkadiy Klyukin}\\
936 Shoreline Dr\\
San Mateo, San Francisco Bay Area, CA}

\signature{Your Name}

\begin{document}

\begin{letter}{\textbf{Citi Talent Acquisition Team} \\
                
                New York }


\opening{Dear Citi Hiring Manager,}

I am writing to express my interest in the Trader - C13, VP, Rates Exotics position at Citi Bank. With over a decade of experience in the financial markets, specializing in liquidity provision, risk management, and trading infrastructure development, I am excited about the opportunity to contribute to Citi Bank's esteemed trading team.

My professional journey has been marked by a consistent track record of exceeding PnL and market share KPIs, most notably achieving the #1 market position locally and #3 internationally among peers. My expertise spans a broad spectrum of financial instruments, including USD, EUR, GBP, JPY, CNY, and CNH, as well as EMEA IR derivatives. I have honed my skills in market making for Cap/Floor, IRS, OIS, xCCY, and STIR FX swaps, among others, and have successfully managed portfolios within various risk parameters, including dv01, credit, basis risk, and VaR.

One of my key projects involved the development and implementation of an Interest Rates Option pricing engine with volatility surface calibration using the Black-76 model. This initiative, along with the launch of new instruments and the integration of innovative XVA approaches, has significantly enhanced trading efficiency and profitability.

My technical acumen is supported by a strong foundation in quantitative finance, as evidenced by my certifications: CQF, FRM, SIE, and CFA. I am proficient in a range of tools and languages, including C#, Python, .NET, and Bloomberg, which I believe aligns well with the qualifications sought for this role.

Citi's reputation for strong governance, responsible finance, and innovative trading solutions resonates with my professional values and aspirations. I am particularly drawn to the bank's global presence and commitment to developing its trading franchise. I am eager to bring my analytical skills, market knowledge, and passion for finance to Citi Bank, where I aim to drive revenue growth and foster key relationships.

I am looking forward to the opportunity to discuss how my background, skills, and enthusiasms can be in sync with the dynamic team at Citi. Thank you for considering my application. I am available at your earliest convenience for an interview.

Sincerely,\\
Arkadiy Klyukin
\end{letter}

\end{document}

% Dear Sir/Madam
% I am very excited to apply to this vacancy. I am going to utilize my strong quantitative skills, extremely fast learning ability and my passion by making a very significant contribution to your firm. My experience in financial markets is almost 6 years, during this period I managed to work at all primary areas of financial markets. 
% Russian derivatives market had been growing very fast during past decade. Being employed by top banks I gained extensive experience in implementing from scratch and maintaining of existing derivative products and whole busyness lines of financial products. E.g. linear derivatives with fx, interest rates, commodities as underlying; derivatives with contingent claims; structured products; exotic derivatives. In those processes I have been deeply involved in elaboration of major and minor aspects of derivatives setup including regulations, legal and taxes, developing of procedures, integrating with internal accounting frameworks and front/back office systems. My responsibilities always include resolving all the issues with market participants related with derivative busyness, so I have a lot of experience in negotiating with clients, dealers, technical vendors and regulatory agencies. 
% I would like to emphasize, best western practices are widely used on the trading floors I work on, because people who built those and continue to develop came from global western banks. Therefore, my knowledge and my experience are the same as employees of global western banks have. I have two higher degrees in finance and mathematics from leading Russian universities; I am also in process of passing CFA and FRM certificates, which are the best and well known certificates in the industry. The experience gained, as well as my personal skills, helps me to bring results every day, regardless of whether the tasks are the main responsibilities for me or whether I carry out non-primary duties. Reliability, extremely fast learning ability and passion are my advantages in comparison with other employees. But I do not stop here. At the moment I understand that the next step is transition to another financial institution with more opportunities and space for greater impact from me.
% I am completely sure that I am suitable for this role. I meet all the requirements with extended knowledge of all the concepts and practices used in financial markets from market microstructure with most modern technical trends to legal and regulatory aspects, ISDA/RISDA structures, EMIR and MiFID regulations, applying of all the XVA concepts to pricing in complicated structured instruments. I am confident that i am the person who will acclimate very fast and will add value to the company continuously. 
% Thank you for your time and interest, I have attached my CV and hope to hear from you soon.

% Yours faithfully,
% Arkadiy Klyukin
