%-------------------------
% Resume in Latex
% Author : Arkadiy Klyukin
% Github : https://github.com/AA-Kl
%------------------------

\documentclass[letterpaper,hidelinks]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{etoolbox}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{kpfonts}
\usepackage{pifont}
\usepackage{ragged2e}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
%\fancyfoot{} %when no page numbering needed
%\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\renewcommand*\ttdefault{lmvtt}
\renewcommand*\familydefault{\ttdefault} %% Only if the base font of the document is to be typewriter style
\usepackage[T1]{fontenc}

% Adjust margins
\addtolength{\oddsidemargin}{-0.77in}
\addtolength{\evensidemargin}{-0.77in}
\addtolength{\textwidth}{1.55in}
\addtolength{\topmargin}{-0.85in}
\addtolength{\textheight}{1.8in}
% \addtolength{\textheight}{1.5in}

\addtolength{\headwidth}{\marginparsep}
\addtolength{\headwidth}{35mm}
\fancyhead[R]{\small{Based:\\ Bay Area, CA \\ Seattle, WA}}
% \fancyfoot[L]{\textit{\small{$\mathbb{}^\ast$ Successfully completed all three levels of the CFA program, currently in the process of obtaining membership}}}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{\vspace{-10pt}\bfseries\raggedright\Large\color{black}}{}{0em}{}[\color{black}\titlerule\vspace{-6pt}]

% Custom commands
\newcommand{\resumeItemRoutine}[1]{
  \item[\small\ding{223}]\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemProject}[1]{
  \item[\small\ding{51}]\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \text{\small#3} & \text{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%
\begin{document}

%----------HEADING-----------------


\begin{center}
  \hspace{-0.4cm}
  % \textbf{\fontfamily{bch}\Huge{Arkadiy Klyukin, CQF, FRM}} \\ \vspace{4pt}
  % \textbf{\fontfamily{pcr}\Huge{Arkadiy Klyukin, CQF, FRM}} \\ \vspace{4pt}
  % \textbf{\fontfamily{lmss}\Huge{Arkadiy Klyukin, CQF, FRM}} \\ \vspace{4pt}
  % \textbf{\Huge{Arkadiy Klyukin, CFA$\mathbb{}^\ast$, CQF, FRM}\\} \\ \vspace{1pt}
  \textbf{\Huge{Arkadiy Klyukin, CQF, FRM, CFA}\\} \\ \vspace{1pt}
  % \textbf{\fontfamily{put}\Huge{Arkadiy Klyukin, CQF, FRM}} \\ \vspace{4pt}
 
  \small
  \faMobile* \hspace{.5pt} \href{tel:+16508888387}{650 888 8387}
  $|$
  \faAt \hspace{.5pt} \href{mailto:arkadiy.klyukin@gmail.com}{arkadiy.klyukin@gmail.com}
  $|$
  \faGlobeAmericas \hspace{.5pt} \href{https://aa-kl.github.io}{aa-kl.github.io}
  $|$
  \faGithub \hspace{.5pt} \href{https://github.com/aa-kl}{aa-kl}
  $|$
  \faLinkedinIn \hspace{.5pt} \href{https://www.linkedin.com/in/aa-kl}{aa-kl}
  $|$
  \faTelegramPlane \hspace{.5pt} \href{https://t.me/aa_tgm}{@aa\_tgm}
\end{center}



%-----------About-----------------	    
\vspace{-27pt}
\section{Summary}
{\hspace{0.1in}
\raggedright{\leftskip.11in Unique blend of expertise in trading, market microstructure, software development, derivatives structuring. Proven track record in advising on complex financial products, building trading environments, optimizing desk operations, and imple-\\menting new financial products and instruments. Strong background in quantitative finance, programming (C\#, Python, VBA), and global market operations. Passionate about driving innovation in financial technology and delivering value.
\\}
}
%-----------Experience-----------------
\vspace{-6pt}
\section{Experience}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeSubheading
{\textbf{\large{Russell Investments,}\small\normalfont{ global investment management firm; dedicated FX\&STIR, FI\&Equity trading desks}}}{\textbf{Aug 2024 \textbf{--} present}}
{\textbf{FX and IR Trader\,/\,Tech Lead \enspace|\enspace FX and STIR desk, Capital Markets department}}{\textbf{Seattle, US}}

\vspace{1pt}
\resumeItemListStart
\resumeItemRoutine{Developed and implemented trading strategies for FX and STIR markets, integrating advanced analytics and automation.}
\resumeItemRoutine{Managed FX overlay and client fund positions, optimizing funding and roll strategies to reduce transaction costs.}
\resumeItemRoutine{Streamlined electronic trading workflows, enhancing connectivity with ECNs, trading venues, and custodians.}
%\resumeItemRoutine{Provided market insights and trade ideas to portfolio managers, enhancing decision-making processes.}
\resumeItemRoutine{Designed and implemented risk management frameworks to monitor limits utilization by types of exposure.}
\resumeItemRoutine{Led the integration of new trading technologies, improving execution speed and reducing operational risks.}
\vspace{2pt}\\
\hspace{-13pt}\textbf{Relevant Projects:}
\vspace{-3pt}
\resumeItemProject{Developed a pricing tool for FX Swaps, improving pre-trade market discovery and reducing trading costs (VBA, Python, Bbg API).}
\resumeItemProject{Analyzed TCA reports for STIR products, identified valuation model flaws and recovered significant PnL discrepancies.}
\resumeItemProject{Implemented automated reporting tools to streamline performance tracking and compliance monitoring.}
\resumeItemListEnd

\vspace{-6pt}
\hspace{0cm}%\titlerule
\vspace{-6pt}

\resumeSubheading
{\textbf{\large{Gazprombank,}\small\normalfont{ one of the largest domestic banks with an extensive international market presence}}}{\textbf{Oct 2018 \textbf{--} Jan 2023}}
{\textbf{Interest Rates Trader\,/\,Derivatives Structuring \enspace|\enspace Fixed Income, Currencies and Commodities desk}}{\textbf{Moscow, RF}}

\vspace{1pt}
\resumeItemListStart
\resumeItemRoutine{Designed and implemented tailored derivatives products, including swaps, options, and structured notes.}
\resumeItemRoutine{Developed pricing engines and trading tools, enhancing desk efficiency and market competitiveness.}
\resumeItemRoutine{Collaborated with legal and tax teams on regulatory transitions, including Libor Fallback and SOFR adoption.}
\resumeItemRoutine{Consistently exceeded PnL targets while managing risk across multiple portfolios and market segments.}
\resumeItemRoutine{Provided liquidity in G10 and CIS STIR, FX Swaps, IRS, OIS, xCCY, and IR options/swaptions.}
\resumeItemRoutine{Worked closely with institutional clients to design and execute customized financial solutions.}
\resumeItemRoutine{Optimized trading algorithms to improve execution quality and reduce slippage.}
\resumeItemRoutine{Participated in the development of new financial products, including Key Rate IRS and FX-implied swaps.}
\vspace{2pt}\\
\hspace{-13pt}\textbf{Relevant Projects:}
\vspace{-3pt}
\resumeItemProject{Built an Interest Rates Option pricing engine with volatility surface calibration (Black-76).}
\resumeItemProject{Launched new derivatives products, including Key Rate IRS and FX-implied swaps, tailored to client needs.}
\resumeItemProject{Integrated advanced XVA approaches, exploiting arbitrage opportunities and improving risk management.}
\resumeItemProject{Developed tools for real-time risk monitoring and portfolio optimization.}
%\resumeItemProject{Developed IR pricing tools, launched providing liquidity in IR products to Bloomberg screen and bbti (C\#, VBA, Bbg API)}
\resumeItemListEnd

\vspace{-6pt}
\hspace{0cm}%\titlerule
\vspace{-6pt}

\resumeSubheading
{\textbf{\large{Promsvyazbank,}\small\normalfont{ one of the top privately held local banks, with cutting-edge technologies in trading}}}{\textbf{Nov 2012 \textbf{--} Sep 2018}}
{\textbf{Head of Electronic FX Trading \enspace|\enspace electronic FX and Commodities trading desk}}{\textbf{Moscow, RF}}

\vspace{1pt}
\resumeItemListStart
\resumeItemRoutine{Developed and deployed electronic trading systems, achieving top market share in FX and STIR markets.}
\resumeItemRoutine{Managed risk and provided liquidity in G10 and CIS currencies, leveraging advanced algorithms and analytics.}
\resumeItemRoutine{Supervised a team of traders and developers, driving innovation and improving client outcomes.}
%\resumeItemRoutine{Provided liquidity to ECNs, corporate clients, and retail customers through single-bank trading platform.}
\resumeItemRoutine{Designed and implemented statistical arbitrage strategies, enhancing profitability.}
\resumeItemRoutine{Collaborated with infrastructure vendors to optimize trading system performance and reduce latency.}
%\resumeItemRoutine{Monitored and managed risk in commodities transactions, including energy, agricultural, and metals trading.}
\vspace{2pt}\\
\hspace{-13pt}\textbf{Relevant Projects:}
\vspace{-3pt}
\resumeItemProject{Built a smart order matching engine and integrated it with ECNs and trading platforms (C\#, FIX, SQL).}
\resumeItemProject{Optimized trading infrastructure by colocating systems in LD4 and MOEX, reducing latency significantly.}
\resumeItemProject{Developed a proprietary trading application for FX basket trading, enhancing client engagement.}
\resumeItemProject{Implemented real-time monitoring tools for market data and trade execution.}
\resumeItemListEnd
\resumeSubHeadingListEnd


%-----------EDUCATION-----------
\vspace{-10pt}
\section{Education}
\vspace{1pt}
\resumeSubHeadingListStart
\resumeSubheading
{{CQF Institute, Fitch | Quantitative finance programm, Leading Professor: Dr. Paul Wilmott}}{London, UK\vspace{-2pt}}
{Quantitative Finance Charter}{Jan 2022 \textbf{--} Jul 2022\vspace{4pt}}
\resumeSubheading
{{New Economic School | Programm in partnership with Morgan Stanley}}{Moscow, RF\vspace{-2pt}}
{Masters in Finance}{Sep 2013 \textbf{--} Jul 2015\vspace{4pt}}
\resumeSubheading
{{Moscow Engineering Physics Institute "MEPHI" | Applied Maths in Economics programm}}{Moscow, RF\vspace{-2pt}}
{Economist Mathematician}{Sep 2007 \textbf{--} Jul 2012}
\resumeSubHeadingListEnd

%-----------CERTIFICATES-----------
\vspace{-4pt}
\section{Certificates}
\resumeSubHeadingListStart
\small{\item{
  \begin{tabularx}{0.96\textwidth} { 
     >{\centering\arraybackslash\hsize=.33\hsize}X 
    || >{\centering\arraybackslash\hsize=.26\hsize}X 
    || >{\centering\arraybackslash\hsize=.35\hsize}X  
    || >{\centering\arraybackslash\hsize=.23\hsize}X } 
    % \textbf{CFA} Charter$\mathbb{}^\ast$, \textbf{CFA Institute} & 
    \textbf{CFA} Charter, \textbf{CFA Institute} & 
    \textbf{FRM} Charter, \textbf{GARP} & 
    \textbf{CQF} Certificate, \textbf{CQF Institute} & 
    \textbf{SIE} Passed, \textbf{FINRA}
    % \textbf{SIE} Passed, \textbf{Series 7} Candidate, \textbf{FINRA}
  \end{tabularx}
% \begin{flushleft} SIE Passed, \textbf{FINRA} \end{flushleft}
% \begin{center} FRM Certified, \textbf{GARP} \end{center} 
% \begin{flushright} CFA Level III Candidate, \textbf{CFA Institute} \end{flushright}
% {SIE Passed, \textbf{FINRA}}  %\vspace{2pt}
% {FRM Certified, \textbf{GARP}}  %\vspace{2pt}
% {CFA Level III Candidate, \textbf{CFA Institute}} %$|$ \vspace{2pt}
}}
\resumeSubHeadingListEnd

%-----------Skills-----------------
\vspace{-11pt}
\section{Skills}
\resumeSubHeadingListStart
\small{\item{
              % \textbf{{Soft:}}{ thorough attention to detail, team player, under pressure decisionmaking, multitasking, self-motivated to learn\\} %$|$ \vspace{2pt}
              \textbf{{Math:}}{ statistics, econometrics, quantitative finance, portfolio optimization, machine learning, reinforcement learning\\} %$|$ \vspace{2pt}
              \textbf{{Programming:}}{ C\#, Python, .NET, QuantLib, QuickFIX, sklearn, pyfolio, Git, Unix/Linux, WPF, sockets, multithreading, bash, SQL, VBA,\LaTeX, Numerix, Calypso, Murex, Misys Summit, Refinitiv, Bloomberg, MarketAxess, Tradeweb, FXall, FXC, Reuters Dealing\\} %$|$ %\vspace{2pt}
              \textbf{{Protocols:}}{ FIX, FAST, PLAZAII, numerous ECN APIs, SSH } %$|$ \vspace{2pt}
              \textbf{{Other Interests:}}{ FPGA, PCB Design, 3D Modelling, Rowing} %$|$ %\vspace{2pt}
              %\textbf{Sports:}{ Rowing, Nordic Skiing} %$|$ %\vspace{2pt}
              %\textbf{Languages:}{ English (Professional), Russian (Native)}
        }}

\resumeSubHeadingListEnd
%-----------Awards-----------------
\vspace{-12pt}
\section{Awards}
\begin{description}%[font=$\bullet$]
  \item{Won trading competition "Algorithmus 2012", nomination "Stable Income" (highest sharpe ratio). \\Asset class: Equities. Strategy: fractal MA, B. Mandelbrot}  
\vspace{-3pt}
\end{description}

\end{document}