\documentclass{letter}

\usepackage{geometry}
\geometry{margin=2cm} % adjust the margin size as needed

\usepackage[T1]{fontenc}
\usepackage{txfonts}


\address{\textbf{Arkadiy Klyukin}\\
936 Shoreline Dr\\
San Mateo, San Francisco Bay Area, CA}

\signature{Your Name}

\begin{document}

\begin{letter}{\textbf{BNY Mellon Talent Acquisition Team} \\
                % Societe Generale \\
                Lake Mary, FL}


\opening{Dear BNY Mellon Hiring Manager,}

I am excited to apply for the Associate position at BNY Mellon Trading Services desk. With five years of experience in derivatives trading, liquidity providing, and portfolio management in both Emerging and Developed markets, as well as extensive expertise in market infrastructure and programming, I am confident that I have the skills and experience necessary to excel in this role.

At previous companies, I was responsible for managing a portfolio of FX and IR derivatives and consistently exceeded PnL goals year over year. I also played a key role in the development of IR Derivatives exchange trade products market section on the biggest Eastern European exchange MOEX. I also served the ALM department to improve portfolios allocation and hedging.

In addition to my experience in market making and portfolio management, I have extensive experience in quantitative modelling and programming. I developed pricing tools and improved trading tools and desk infrastructure. For example, I developed a pricing tools for FX options that allowed for quick and accurate pricing of complex option structures. I also led process of automation of various trading tasks, such as order entry and risk management.

I am confident that my experience and skills make me an excellent candidate for the Associate position at BNY Mellon. Thank you for considering my application, I look forward to the opportunity to discuss my qualifications further.

I hold a valid work visa L2S and am authorized to work in the US.

Sincerely,\\
Arkadiy Klyukin
\end{letter}

\end{document}