\documentclass{letter}

\usepackage{geometry}
\geometry{margin=2cm} % adjust the margin size as needed

\usepackage[T1]{fontenc}
\usepackage{txfonts}


\address{\textbf{Arkadiy Klyukin}\\
San Francisco Bay Area, CA}

\signature{Your Name}

\begin{document}

\begin{letter}{\textbf{Citi Bank Talent Acquisition Team} \\
                % US Bank \\
                New York, NY}


\opening{Dear Citi Hiring Manager,}

I am writing to express my interest in the Rates Trader position at Citi Bank. With 9 years of experience in rates trading and risk management, along with a strong background in market making, liquidity providing, portfolio management in both Emerging and Developed markets currencies and IR derivatives, and a proven track record of exceeding performance metrics, I am confident in my ability to contribute to the success of the team.

In my previous roles, I successfully facilitated client transactions, ran derivatives books, and developed advanced trading tools and infrastructure. My experience in market making, risk management, and project leadership aligns closely with the responsibilities and qualifications outlined in the job description. I would like emphasize that I also played a key role in the development of IR Derivatives franchise; oversaw sales, trading and developers teams; worked extensively on front office processes developement and particularly derivatives-management-part of it, including setting up from scratch and pricing models homologation and validation. I also served the ALM department to improve portfolios allocation and hedging and worked closely with legal and tax teams. Additionally, my certifications in quantitative finance, financial risk management, and securities essentials, along with my proficiency in programming languages and financial software, further validate my qualifications for this role.

I also have had the privilege of working closely with the Citi trading team on a daily basis, collaborating on a wide range of business activities and transactions. Our partnership has been instrumental in driving successful outcomes, from executing complex client trades to managing risks for proprietary books. The strong relationship I have cultivated with the Citi Bank traders has not only facilitated seamless communication and decision-making but has also contributed to the overall success of our trading activities.

I am confident that my experience and skills make me an excellent candidate for the Rates Trader position at Citi. Thank you for considering my application, I look forward to the opportunity to discuss my qualifications further.

Sincerely,\\
Arkadiy Klyukin
\end{letter}

\end{document}