%-------------------------
% Resume in Latex
% Author : Arkadiy Klyukin
% Github : https://github.com/AA-Kl
%------------------------

\documentclass[letterpaper,hidelinks]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{etoolbox}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{kpfonts}
\usepackage{pifont}
\usepackage{ragged2e}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
%\fancyfoot{} %when no page numbering needed
%\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\renewcommand*\ttdefault{lmvtt}
\renewcommand*\familydefault{\ttdefault} %% Only if the base font of the document is to be typewriter style
\usepackage[T1]{fontenc}

% Adjust margins
\addtolength{\oddsidemargin}{-0.77in}
\addtolength{\evensidemargin}{-0.77in}
\addtolength{\textwidth}{1.55in}
\addtolength{\topmargin}{-0.8in}
\addtolength{\textheight}{1.5in}

\addtolength{\headwidth}{\marginparsep}
\addtolength{\headwidth}{35mm}
\fancyhead[R]{\small{Authorized to work\\ in the US, \\ Green Card}}
\fancyfoot[L]{\textit{\small{$\mathbb{}^\ast$ Successfully completed all three levels of the CFA program, currently in the process of obtaining membership}}}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{\vspace{-10pt}\bfseries\raggedright\Large\color{black}}{}{0em}{}[\color{black}\titlerule\vspace{-6pt}]

% Custom commands
\newcommand{\resumeItemRoutine}[1]{
  \item[\small\ding{223}]\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemProject}[1]{
  \item[\small\ding{51}]\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \text{\small#3} & \text{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%
%----------HEADING-----------------
\begin{center}
  \textbf{\Huge{Arkadiy Klyukin, CFA$\mathbb{}^\ast$, CQF, FRM}\\} \\ \vspace{1pt}
  \small
  \faMobile* \hspace{.5pt} \href{tel:+16508888387}{650 888 8387}
  $|$
  \faAt \hspace{.5pt} \href{mailto:arkadiy.klyukin@gmail.com}{arkadiy.klyukin@gmail.com}
  $|$
  \faGlobeAmericas \hspace{.5pt} \href{https://aa-kl.github.io}{aa-kl.github.io}
  $|$
  \faGithub \hspace{.5pt} \href{https://github.com/aa-kl}{aa-kl}
  $|$
  \faLinkedinIn \hspace{.5pt} \href{https://www.linkedin.com/in/aa-kl}{aa-kl}
  $|$
  \faTelegramPlane \hspace{.5pt} \href{https://t.me/aa_tgm}{@aa\_tgm}
\end{center}
%-----------About-----------------	    
\vspace{-27pt}
\section{Summary}
{\hspace{0.1in}
\raggedright{\leftskip.11in
    % ========== Summary Text ==========
An accomplished professional with over 5 years of comprehensive experience in commercial real estate valuation, financial reporting, and capital markets. Recognized for the ability to develop robust valuation models, perform complex financial and statistical analysis, and provide expert advisory services. Demonstrated expertise in managing portfolios within stringent financial limits, utilizing advanced statistical analysis techniques to evaluate trade risk, and leading the adoption of Agile methodologies to accelerate trading tools enhancement. Adept at fostering collaborations with internal and external stakeholders, consistently surpassing PnL and market share key performance indicators, and originating new client relationships. Offering proficiency in Microsoft Office applications, familiarity with US GAAP and IFRS accounting standards, and a strong team player mentality strengthened by excellent communication skills. 
% ==================================    
    \\}
}
%-----------Experience-----------------
\vspace{-8pt}
\section{Experience}
\vspace{1pt}
\resumeSubHeadingListStart
\resumeSubheading
{\textbf{\large{Gazprombank,}\small\normalfont{ one of the largest domestic banks with an extensive international market presence}}}{\textbf{Oct 2018 \textbf{--} Jan 2023}}
{\textbf{Interest Rates Trader | Fixed Income, Currencies and Commodities desk, Capital Markets}}
{\textbf{Moscow, RF}}
\vspace{1pt}
\resumeItemListStart
    % ========== G_Bank Routine ==========
\resumeItemRoutine{Acted as a market maker for a diverse range of financial instruments including Interest Rate Swaps (IRS), Cross-Currency Rate Swaps, Short Term Interest Rates FX swaps, spot currency transactions, and precious metals and commodities transactions.}
\resumeItemRoutine{Managed portfolios within stringent financial limits such as dv01 and VaR thresholds, minimizing basis risk and maintaining credit quality.}
\resumeItemRoutine{Collaborated with the asset/liability management (ALM) department to refine investment allocations, enhance hedging strategies, and optimize funding ratios.}
\resumeItemRoutine{Provided key support to the internal sales team and institutional clients by delivering competitive pricing and actionable trade ideas.}
\resumeItemRoutine{Led the adoption of Agile methodologies to accelerate the enhancement of trading tools and desk infrastructure}
% ==================================
\vspace{2pt}\\
\hspace{-13pt}\textbf{Relevant Projects:}
\vspace{-3pt}
    % ========== G_Bank Projects ==========
\resumeItemProject{Implemented Interest Rates Option pricing engine with volatility surface calibration and modeling.}
\resumeItemProject{Launched new instruments pricing and liquidity providing, in compliance with ISDA regulations.}
\resumeItemProject{Developed IR pricing tools, launched providing liquidity in IR products to Bloomberg screen and bbti.}
\resumeItemProject{Participated in front office system (Calypso) set up and integration from scratch on every level}
% ==================================
\resumeItemListEnd

\vspace{-6pt}
\hspace{0cm}
\vspace{-8pt}

\resumeSubheading
{\textbf{\large{Promsvyazbank,}\small\normalfont{ one of the top privately held local banks, with cutting-edge technologies in trading}}}{\textbf{Nov 2012 \textbf{--} Sep 2018}}
{\textbf{e-FX Trader | electronic FX and Precious Metals trading desk}}
{\textbf{Moscow, RF}}
\vspace{1pt}
\resumeItemListStart
    % ========== P_Bank Routine ==========
\resumeItemRoutine{Executed electronic client trades and provided liquidity in G10, and CIS currencies.}
\resumeItemRoutine{Monitored and managed risk in commodities transactions: energy, agricultural, metals flow trading.}
\resumeItemRoutine{Developed franchise relations with key clients and cultivated new relationships, ensuring the best client experience.}
\resumeItemRoutine{Managed and supervised e-FX sales and programming teams, setting goals, improving client outcomes}
% ==================================
\vspace{2pt}\\
\hspace{-13pt}\textbf{Relevant Projects:}
\vspace{-3pt}
    % ========== P_Bank Projects ==========
\resumeItemProject{Developed feeds collecting and smart order matching engine from scratch.}
\resumeItemProject{Added short term IR liquidity providing/absorbing to/from WL single-bank platform.}
\resumeItemProject{Placed engine segments to LD4, Equinix, MOEX collocations which improved roundtrip dramatically.}
\resumeItemProject{Developed proprietary client-server trading application for FX basket trading}
% ==================================
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-10pt}
\section{Education}
\vspace{1pt}
\resumeSubHeadingListStart
\resumeSubheading
{{CQF Institute, Fitch | Quantitative finance programm, Leading Professor: Dr. Paul Wilmott}}{London, UK\vspace{-2pt}}
{Quantitative Finance Charter}{Jan 2022 \textbf{--} Jul 2022\vspace{4pt}}
\resumeSubheading
{{New Economic School | Morgan Stanley programm, Rector: Dr. Sergey Guriev}}{Moscow, RF\vspace{-2pt}}
{Masters in Finance}{Sep 2013 \textbf{--} Jul 2015\vspace{4pt}}
\resumeSubheading
{{National Research Nuclear University "MEPHI" | Applied Maths in Economics programm}}{Moscow, RF\vspace{-2pt}}
{Economist Mathematician}{Sep 2007 \textbf{--} Jul 2012}
\resumeSubHeadingListEnd

%-----------CERTIFICATES-----------
\vspace{-4pt}
\section{Certificates}
\resumeSubHeadingListStart
\small{\item{
  \begin{tabularx}{0.96\textwidth} { 
     >{\centering\arraybackslash\hsize=.33\hsize}X 
    || >{\centering\arraybackslash\hsize=.26\hsize}X 
    || >{\centering\arraybackslash\hsize=.35\hsize}X  
    || >{\centering\arraybackslash\hsize=.23\hsize}X } 
    \textbf{CFA} Charter$\mathbb{}^\ast$, \textbf{CFA Institute} & 
    \textbf{FRM} Charter, \textbf{GARP} & 
    \textbf{CQF} Certificate, \textbf{CQF Institute} & 
    \textbf{SIE} Passed, \textbf{FINRA}
    % \textbf{SIE} Passed, \textbf{Series 7} Candidate, \textbf{FINRA}
  \end{tabularx}
% \begin{flushleft} SIE Passed, \textbf{FINRA} \end{flushleft}
% \begin{center} FRM Certified, \textbf{GARP} \end{center} 
% \begin{flushright} CFA Level III Candidate, \textbf{CFA Institute} \end{flushright}
% {SIE Passed, \textbf{FINRA}}  %\vspace{2pt}
% {FRM Certified, \textbf{GARP}}  %\vspace{2pt}
% {CFA Level III Candidate, \textbf{CFA Institute}} %$|$ \vspace{2pt}
}}
\resumeSubHeadingListEnd

%-----------Skills-----------------
\vspace{-11pt}
\section{Skills}
%\vspace{1pt}
\resumeSubHeadingListStart
\small{\item{
              % \textbf{{Soft:}}{ thorough attention to detail, team player, under pressure decisionmaking, multitasking, self-motivated to learn\\} %$|$ \vspace{2pt}
              \textbf{{Math:}}{ statistics, econometrics, quantitative finance, portfolio optimization, machine learning, reinforcement learning\\} %$|$ \vspace{2pt}
              \textbf{{Programming:}}{ C\#, Python, .NET, QuantLib, QuickFIX, sklearn, pyfolio, Git, WPF, sockets, multithreading, bash, SQL, VBA, \LaTeX\\} %$|$ %\vspace{2pt}
              \textbf{{Software:}}{ Numerix, Calypso, Murex, Misys Summit, Refinitiv, Bloomberg, Reuters Dealing, 360T, FXAll, FastMatch, Integral, MS Excel\\} %$|$ \vspace{2pt}
              \textbf{{Protocols:}}{ FIX, FAST, PLAZAII, Bloomberg API, numerous ECN APIs, Open AI API, SSH } %$|$ \vspace{2pt}
              \textbf{{Other Interests:}}{ PCB Design, 3D, Rowing} %$|$ %\vspace{2pt}
              %\textbf{Sports:}{ Rowing, Nordic Skiing} %$|$ %\vspace{2pt}
              %\textbf{Languages:}{ English (Professional), Russian (Native)}
        }}

\resumeSubHeadingListEnd
%-----------Awards-----------------
\vspace{-12pt}
\section{Awards}
\begin{description}%[font=$\bullet$]
  \item{Won trading competition "Algorithmus 2012", nomination "Stable Income" (highest sharpe ratio). \\Asset class: Equities. Strategy: fractal MA, B. Mandelbrot}  
\vspace{-3pt}
\end{description}

\end{document} 