\documentclass{letter}

\usepackage{geometry}
\geometry{margin=2cm} % adjust the margin size as needed

\usepackage[T1]{fontenc}
\usepackage{txfonts}


\address{\textbf{Arkadiy Klyukin}\\
936 Shoreline Dr\\
San Mateo, San Francisco Bay Area, CA}

\signature{Your Name}

\begin{document}

\begin{letter}{\textbf{Goldman Sachs Talent Acquisition Team} \\
                
                New York }


\opening{Dear Goldman Sachs Corporate Tresury Hiring Manager,}

I am writing to express my interest in the Corporate Tresury Funding Execution Trader position at Goldman Sachs, as advertised. With a robust background in market making, risk management, and trade execution across various financial instruments and currencies, I am excited about the opportunity to contribute to the Funding Execution team in New York.

My career has been marked by a dedication to providing innovative financing solutions and optimizing trading strategies. I have facilitated client and treasury transactions in multiple currencies and managed portfolios within strict risk limits, consistently exceeding various kinds of KPIs. My experience in developing pricing engines and liquidity provision tools, particularly for interest rate derivatives and FX swaps, aligns closely with the responsibilities of pricing and risk management outlined for this role.

I have a strong understanding of economic, fiscal, and monetary policy, which has been instrumental in generating trade ideas to reduce interest expense and capital consumption while improving liquidity metrics. My proficiency in Excel, including VBA, and my comfort with building and managing financial models will allow me to effectively analyze and interpret complex pricing models at Goldman Sachs.

In addition to my technical skills, I bring a strong work ethic and enthusiasm for financial markets. My qualifications are further supported by certifications such as CQF, FRM, SIE, and CFA, which underscore my commitment to continuous learning and excellence in the field of finance.

I am particularly drawn to this role at Goldman Sachs because of the firm's reputation for innovation and leadership in global markets. I am eager to contribute my expertise to the Funding Execution team and collaborate with colleagues across the firm to deliver superior financing solutions to clients.

Thank you for considering my application. I am looking forward to the opportunity to discuss how my skills and experiences align with the goals of Goldman Sachs. Please feel free to contact me to arrange an interview.

Sincerely,\\
Arkadiy Klyukin
\end{letter}

\end{document}

% Dear Sir/Madam
% I am very excited to apply to this vacancy. I am going to utilize my strong quantitative skills, extremely fast learning ability and my passion by making a very significant contribution to your firm. My experience in financial markets is almost 6 years, during this period I managed to work at all primary areas of financial markets. 
% Russian derivatives market had been growing very fast during past decade. Being employed by top banks I gained extensive experience in implementing from scratch and maintaining of existing derivative products and whole busyness lines of financial products. E.g. linear derivatives with fx, interest rates, commodities as underlying; derivatives with contingent claims; structured products; exotic derivatives. In those processes I have been deeply involved in elaboration of major and minor aspects of derivatives setup including regulations, legal and taxes, developing of procedures, integrating with internal accounting frameworks and front/back office systems. My responsibilities always include resolving all the issues with market participants related with derivative busyness, so I have a lot of experience in negotiating with clients, dealers, technical vendors and regulatory agencies. 
% I would like to emphasize, best western practices are widely used on the trading floors I work on, because people who built those and continue to develop came from global western banks. Therefore, my knowledge and my experience are the same as employees of global western banks have. I have two higher degrees in finance and mathematics from leading Russian universities; I am also in process of passing CFA and FRM certificates, which are the best and well known certificates in the industry. The experience gained, as well as my personal skills, helps me to bring results every day, regardless of whether the tasks are the main responsibilities for me or whether I carry out non-primary duties. Reliability, extremely fast learning ability and passion are my advantages in comparison with other employees. But I do not stop here. At the moment I understand that the next step is transition to another financial institution with more opportunities and space for greater impact from me.
% I am completely sure that I am suitable for this role. I meet all the requirements with extended knowledge of all the concepts and practices used in financial markets from market microstructure with most modern technical trends to legal and regulatory aspects, ISDA/RISDA structures, EMIR and MiFID regulations, applying of all the XVA concepts to pricing in complicated structured instruments. I am confident that i am the person who will acclimate very fast and will add value to the company continuously. 
% Thank you for your time and interest, I have attached my CV and hope to hear from you soon.

% Yours faithfully,
% Arkadiy Klyukin
