\documentclass{letter}

\usepackage{geometry}
\geometry{margin=2cm} % adjust the margin size as needed

\usepackage[T1]{fontenc}
\usepackage{txfonts}


\address{\textbf{Arkadiy Klyukin}\\
San Francisco Bay Area, CA}

\signature{Your Name}

\begin{document}

\begin{letter}{\textbf{Jane Street Talent Acquisition Team} \\
                % US Bank \\
                San Francisco, CA}
\opening{Dear Hiring Manager,}

I am writing to express my interest in the Equity Options Floor Trader position. With over nine of experience in market making, risk management, and electronic trading, I am excited about the opportunity to contribute to your floor trading team in San Francisco.

In my previous roles, I have successfully facilitated client transactions in IR Options (Caps/Floors/Swaptions), managed portfolios, and developed trading tools to enhance efficiency and profitability. My experience in electronic trading includes providing liquidity in G10 and CIS currencies, monitoring and managing risk in commodities transactions, and developing proprietary client-server trading applications for FX basket trading. I have a proven track record of achieving PnL goals and improving trading tools and desk infrastructure to increase efficiency in electronic trading environments..

I am highly analytical, detail-oriented, and possess strong communication skills, which I believe are essential for effectively relaying real-time information on the trading floor and collaborating with team members. My track record of exceeding PnL and market share KPIs demonstrates my ability to thrive in a fast-paced environment while maintaining a focus on risk management and relationship building.

I am particularly drawn to the commitment to innovation and collaboration, and I am eager to contribute my problem-solving skills and industry expertise to help drive the success of the floor trading team.

I look forward to the opportunity to discuss how my background and skills align with the needs of your team. Thank you for considering my application.

Sincerely,\\
Arkadiy Klyukin
\end{letter}

\end{document}