%-------------------------
% Resume in Latex
% Author : Arkadiy Klyukin
% Github : https://github.com/AA-Kl
%------------------------

\documentclass[letterpaper,hidelinks]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{etoolbox}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{kpfonts}
\usepackage{pifont}
\usepackage{ragged2e}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
%\fancyfoot{} %when no page numbering needed
%\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\renewcommand*\ttdefault{lmvtt}
\renewcommand*\familydefault{\ttdefault} %% Only if the base font of the document is to be typewriter style
\usepackage[T1]{fontenc}

% Adjust margins
\addtolength{\oddsidemargin}{-0.77in}
\addtolength{\evensidemargin}{-0.77in}
\addtolength{\textwidth}{1.55in}
\addtolength{\topmargin}{-0.8in}
\addtolength{\textheight}{1.5in}

\addtolength{\headwidth}{\marginparsep}
\addtolength{\headwidth}{35mm}
\fancyhead[R]{\small{Authorized to work\\ in the US, \\ Green Card}}
\fancyfoot[L]{\textit{\small{$\mathbb{}^\ast$ Successfully completed all three levels of the CFA program, currently in the process of obtaining membership}}}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{\vspace{-10pt}\bfseries\raggedright\Large\color{black}}{}{0em}{}[\color{black}\titlerule\vspace{-6pt}]

% Custom commands
\newcommand{\resumeItemRoutine}[1]{
  \item[\small\ding{223}]\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemProject}[1]{
  \item[\small\ding{51}]\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \text{\small#3} & \text{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%
\begin{document}

%----------HEADING-----------------


\begin{center}
  % \hspace{2cm}
  % \textbf{\fontfamily{bch}\Huge{Arkadiy Klyukin, CQF, FRM}} \\ \vspace{4pt}
  % \textbf{\fontfamily{pcr}\Huge{Arkadiy Klyukin, CQF, FRM}} \\ \vspace{4pt}
  % \textbf{\fontfamily{lmss}\Huge{Arkadiy Klyukin, CQF, FRM}} \\ \vspace{4pt}
  \textbf{\Huge{Arkadiy Klyukin, CFA$\mathbb{}^\ast$, CQF, FRM}\\} \\ \vspace{1pt}
  % \textbf{\fontfamily{put}\Huge{Arkadiy Klyukin, CQF, FRM}} \\ \vspace{4pt}
 
  \small
  \faMobile* \hspace{.5pt} \href{tel:+16508888387}{650 888 8387}
  $|$
  \faAt \hspace{.5pt} \href{mailto:arkadiy.klyukin@gmail.com}{arkadiy.klyukin@gmail.com}
  $|$
  \faGlobeAmericas \hspace{.5pt} \href{https://aa-kl.github.io}{aa-kl.github.io}
  $|$
  \faGithub \hspace{.5pt} \href{https://github.com/aa-kl}{aa-kl}
  $|$
  \faLinkedinIn \hspace{.5pt} \href{https://www.linkedin.com/in/aa-kl}{aa-kl}
  $|$
  \faTelegramPlane \hspace{.5pt} \href{https://t.me/aa_tgm}{@aa\_tgm}
\end{center}



%-----------About-----------------	    
\vspace{-27pt}
\section{Summary}
{\hspace{0.1in}
\raggedright{\leftskip.11in Results-driven Interest Rates and FX derivatives trader with a proven track record in market making, portfolio manage- ment, and electronic trading. Experienced in market making in interest rates, FX, and commodities. Consistently exceeding PnL and market share KPIs. Skilled in developing and implementing new products, derivatives structuring, regulatory frameworks, and technical market microstructure. Strong background in quantitative finance, machine learning, and programming languages such as C\#, Python, and .NET. Developed several innovative tools for manual and automatic trading, auxiliary tools for discretionary trading, multithreaded algorithms for high-frequency trading. Certified in quantitative finance, financial analysis, and financial risk management.\\}
% \raggedright{\leftskip.11in Interest Rates and FX derivatives trader with extensive hands-on experience in market making and quantitative research, systematic trading, derivatives structuring and programming (Python, VBA, C\#) Built and deployed various types of algorithms and trading models: market making, order execution algorithms, decision-based trading, and statistical arbitrage. Comprehensive knowledge of sell-side risk management systems, capital markets technical microstructure. Developed several innovative tools for manual and automatic trading, auxiliary tools for discretionary trading, multithreaded algorithms for high-frequency trading, incorporated machine learning techniques into market making algos. Constantly focused on value addition to everything that is within reach, deep-diving into every aspect.\\}
}
%-----------Experience-----------------
\vspace{-8pt}
\section{Experience}
\vspace{1pt}
\resumeSubHeadingListStart

\resumeSubheading
{\textbf{\large{Gazprombank,}\small\normalfont{ one of the largest domestic banks with an extensive international market presence}}}{\textbf{Oct 2018 \textbf{--} Jan 2023}}
{\textbf{Interest Rates Trader | Fixed Income, Currencies and Commodities desk, Capital Markets}}{\textbf{Moscow, RF}}

\vspace{1pt}
\resumeItemListStart
\resumeItemRoutine{Facilitating client transactions by providing liquidity in USD, EUR, GBP, JPY, CNY and CNH and EMEA IR derivatives.}
\resumeItemRoutine{Market making in Cap/Floor, IRS, OIS, xCCY, STIR FX swaps, spot currency transactions, precious metals, commodities.}
% \resumeItemRoutine{Flow rates trading G10, CIS, CNH xCCYs}
% \resumeItemRoutine{Liquidity providing in IR Swaps and IR Options with continuously growing market share.}
\resumeItemRoutine{Managing portfolios abiding various types of limits: dv01, credit, basis risk, VaR, and counterparty specific limits.}
\resumeItemRoutine{Consistently exceeded PnL and market share KPIs, growing permanently (\#1 on local market, \#3 including international peers)}
\resumeItemRoutine{Working closely with asset/liability management (ALM) department, improving allocations, hedging and funding ratios.}
\resumeItemRoutine{Providing internal sales team and institutional clients with pricing, trade ideas, participating in tailored products design.}
\resumeItemRoutine{Identification and interpreting statistical data to assess trade risk, and generation and execution trade ideas.}
\resumeItemRoutine{Improving trading tools and desk infrastructure, developing and optimizing in-house technology to increase efficiency.}
\resumeItemRoutine{Working in collaboration with legal and tax teams on technical topics such as Libor Fallback protocol and SOFR transition.}
% \resumeItemRoutine{Participation and collaboration in the development of IR Derivatives products market section on local exchange MOEX}
\vspace{2pt}\\
\hspace{-13pt}\textbf{Relevant Projects:}
\vspace{-3pt}
\resumeItemProject{Elaborated and implemented Interest Rates Option pricing engine with volatility surface calibration and modeling (Black-76)}
\resumeItemProject{Launched new instruments pricing and liq providing (Key Rate IRS and Caps/Floors, FX-implied swap, etc), ISDA regulations.}
\resumeItemProject{Implemented new XVA (FVA and ColVA) approaches for rub market instruments, exploited arbitrage between approaches.}
\resumeItemProject{Developed IR pricing tools, launched providing liquidity in IR products to Bloomberg screen and bbti (C\#, VBA, Bbg API)}
\resumeItemProject{Participation in front office system (Calypso) set up and integration from scratch on every level, from pricing models homologation and validation to straight-through processing and workstation tools and reports design.}
\resumeItemListEnd

\vspace{-6pt}
\hspace{0cm}%\titlerule
\vspace{-8pt}
% \hspace{0cm}\noindent\rule{19cm}{0.2pt}
% \vspace{50pt}

\resumeSubheading
{\textbf{\large{Promsvyazbank,}\small\normalfont{ one of the top privately held local banks, with cutting-edge technologies in trading}}}{\textbf{Nov 2012 \textbf{--} Sep 2018}}
{\textbf{e-FX Trader | electronic FX and Commodities trading desk}}{\textbf{Moscow, RF}}

\vspace{1pt}
\resumeItemListStart
\resumeItemRoutine{Electronic client trades execution and liquidity providing in G10, and CIS currencies (Short Term IR and FX Spot/FX Swaps)}
\resumeItemRoutine{Monitoring and managing risk in commodities transactions: energy, agricultural, metals flow trading.}
% \resumeItemRoutine{Electronic market making, FX Swaps, and FX Spot}
\resumeItemRoutine{Achieving PnL goals, developed and integrated electronic pricing engine which led to becoming top 1-2 market share.}
\resumeItemRoutine{Providing liquidity to ECNs, corp and retail customers, other banks single-bank trading platforms (white label solutions)}
% \resumeItemRoutine{Institutional clients/dealers/WL clients helpdesk. Liaising with the sales team}
\resumeItemRoutine{Developing franchise relations with key clients and cultivating new relationships, ensuring best client experience.}
\resumeItemRoutine{Managing and supervising two members e-FX sales team and three programmers, setting goals, improving client outcomes.}
\resumeItemRoutine{Coverage of all business and technical aspects of electronic trading (prime brokers, legal, infrastructure vendors)}
\vspace{2pt}\\
\hspace{-13pt}\textbf{Relevant Projects:}
\vspace{-3pt}
\resumeItemProject{Developed feeds collecting and smart order matching engine from scratch (C\#, FIX, SQL)}
\resumeItemProject{Added short term IR liquidity providing/absorbing to/from WL single-bank platform.}
\resumeItemProject{Established transition to UDP protocols, added feeds from the exchange-traded D1 derivatives market (FAST, Plaza)}
\resumeItemProject{Placed engine segments to LD4, Equinix, MOEX collocations which improved roundtrip dramatically.}
\resumeItemProject{Developed proprietary client-server trading application for FX basket trading (FIX, Sockets, WPF)}
\resumeItemProject{Integrated statistical arbitrage algorithms (CME-MOEX), retail customers flow, and high correlated ccy-pairs liquidity extraction into the order routing and matching circuit.}
\resumeItemListEnd
\resumeSubHeadingListEnd


%-----------EDUCATION-----------
\vspace{-10pt}
\section{Education}
\vspace{1pt}
\resumeSubHeadingListStart
\resumeSubheading
{{CQF Institute, Fitch | Quantitative finance programm, Leading Professor: Dr. Paul Wilmott}}{London, UK\vspace{-2pt}}
{Quantitative Finance Charter}{Jan 2022 \textbf{--} Jul 2022\vspace{4pt}}
\resumeSubheading
{{New Economic School | Morgan Stanley programm, Rector: Dr. Sergey Guriev}}{Moscow, RF\vspace{-2pt}}
{Masters in Finance}{Sep 2013 \textbf{--} Jul 2015\vspace{4pt}}
\resumeSubheading
{{National Research Nuclear University "MEPHI" | Applied Maths in Economics programm}}{Moscow, RF\vspace{-2pt}}
{Economist Mathematician}{Sep 2007 \textbf{--} Jul 2012}
\resumeSubHeadingListEnd

%-----------CERTIFICATES-----------
\vspace{-4pt}
\section{Certificates}
\resumeSubHeadingListStart
\small{\item{
  \begin{tabularx}{0.96\textwidth} { 
     >{\centering\arraybackslash\hsize=.33\hsize}X 
    || >{\centering\arraybackslash\hsize=.26\hsize}X 
    || >{\centering\arraybackslash\hsize=.35\hsize}X  
    || >{\centering\arraybackslash\hsize=.23\hsize}X } 
    \textbf{CFA} Charter$\mathbb{}^\ast$, \textbf{CFA Institute} & 
    \textbf{FRM} Charter, \textbf{GARP} & 
    \textbf{CQF} Certificate, \textbf{CQF Institute} & 
    \textbf{SIE} Passed, \textbf{FINRA}
    % \textbf{SIE} Passed, \textbf{Series 7} Candidate, \textbf{FINRA}
  \end{tabularx}
% \begin{flushleft} SIE Passed, \textbf{FINRA} \end{flushleft}
% \begin{center} FRM Certified, \textbf{GARP} \end{center} 
% \begin{flushright} CFA Level III Candidate, \textbf{CFA Institute} \end{flushright}
% {SIE Passed, \textbf{FINRA}}  %\vspace{2pt}
% {FRM Certified, \textbf{GARP}}  %\vspace{2pt}
% {CFA Level III Candidate, \textbf{CFA Institute}} %$|$ \vspace{2pt}
}}
\resumeSubHeadingListEnd

%-----------Skills-----------------
\vspace{-11pt}
\section{Skills}
%\vspace{1pt}
\resumeSubHeadingListStart
\small{\item{
              % \textbf{{Soft:}}{ thorough attention to detail, team player, under pressure decisionmaking, multitasking, self-motivated to learn\\} %$|$ \vspace{2pt}
              \textbf{{Math:}}{ statistics, econometrics, quantitative finance, portfolio optimization, machine learning, reinforcement learning\\} %$|$ \vspace{2pt}
              \textbf{{Programming:}}{ C\#, Python, .NET, QuantLib, QuickFIX, sklearn, pyfolio, Git, Unix/Linux, WPF, sockets, multithreading, bash, SQL, VBA,\LaTeX, Numerix, Calypso, Murex, Misys Summit, Refinitiv, Bloomberg, Reuters Dealing, MS Excel \\} %$|$ %\vspace{2pt}
              \textbf{{Protocols:}}{ FIX, FAST, PLAZAII, numerous ECN APIs, SSH } %$|$ \vspace{2pt}
              \textbf{{Other Interests:}}{ FPGA, PCB Design, 3D Modelling, Rowing} %$|$ %\vspace{2pt}
              %\textbf{Sports:}{ Rowing, Nordic Skiing} %$|$ %\vspace{2pt}
              %\textbf{Languages:}{ English (Professional), Russian (Native)}
        }}

\resumeSubHeadingListEnd
%-----------Awards-----------------
\vspace{-12pt}
\section{Awards}
\begin{description}%[font=$\bullet$]
  \item{Won trading competition "Algorithmus 2012", nomination "Stable Income" (highest sharpe ratio). \\Asset class: Equities. Strategy: fractal MA, B. Mandelbrot}  
\vspace{-3pt}
\end{description}

\end{document} 